OCMu64: a solver for One-sided Crossing Minimization

### 2024-06-20 tex/description.tex
non-empty
9+10

\begin{remark}
  Let $u$ and $v$ satisfy $r(u,v) \leq 0$.
  When $N(u)=N(v)$ or more generally $\w_u=\w_v$, we can glue $u$ and $v$: $u\g v$.
  Otherwise, there is a multiset $\mathcal X\subseteq A$ such that $(u, X, v)$ is
  better than $(u,v,X)$ and $(X,u,v)$.
\end{remark}
This means that there is no `strong gluing'.
\begin{lemma}[Practical gluing]\label{pg}
  Let $u$ and $v$ satisfy $r(u,v)\leq 0$ and $u\b v$.
  A subset $X\subseteq B-\{u,v\}$ is \emph{blocking} when $c(u, X, v)$ is at
  least as good as $c(u,v,X)$ and $c(X,u,v)$.
  If there is no blocking set, then $u \g v$.
\end{lemma}
Again such sets $X$ can be found or proven to not exist using a knapsack
algorithm: add points $P_x = (r(u, x), r(x, v))$ and search for a non-empty
set summing to $\leq{}(0,0)$.

>>>>

\begin{remark}
  Let $u$ and $v$ satisfy $r(u,v) < 0$.
  When $N(u)=N(v)$ or more generally $\w_u=\w_v$, we can glue $u$ and $v$: $u\g v$.
  Otherwise, there is an $X : A\to \mathbb R^{\geq 0}$ such that $(u, X, v)$ is
  better than $(u,v,X)$ and $(X,u,v)$.
\end{remark}
This means that there is no `strong gluing'.
\begin{lemma}[Practical gluing]\label{pg}
  Let $u$ and $v$ satisfy $u\b v$.
  A non-empty subset $X\subseteq B-\{u,v\}$ is \emph{blocking} when $c(u, X, v)$ is at
  least as good as $c(u,v,X)$ and $c(X,u,v)$.
  If there is no blocking set, then $u \g v$.
\end{lemma}
Again such sets $X$ can be found or proven to not exist using a knapsack
algorithm: add points $P_x = (r(u, x), r(x, v))$ and search for a non-empty
set summing to $\leq{}(0,0)$.
